### 2013-06-20 trunk/network-science/paper.tex

\documentclass[a4paper,twocolumn,10pt]{article}
\usepackage{multicol}
\usepackage{listings}
\usepackage{fourier}
\usepackage{amsmath}

\usepackage{tikz}
\tikzstyle{every picture}+=[remember picture]
\usetikzlibrary{arrows,decorations.pathreplacing,decorations.markings}
\usepackage{listings}
\lstset{
	numbers=left,
	basicstyle=\small\ttfamily,
	numberstyle=\it\scriptsize\sffamily,
	keywordstyle=\bf,
	commentstyle=\color{red!50!green!50!blue!50},
	frame=single,
	%breaklines=true,
}

\usepackage{geometry}
\geometry{left=0.7cm,right=0.7cm,top=0.7cm,bottom=1.3cm}
%\linespread{1.0}

\AtBeginDocument{%
	\setlength\abovedisplayskip{3pt}
	\setlength\belowdisplayskip{3pt}
}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{5pt}{5pt}
\titlespacing{\subsection}{0pt}{5pt}{5pt}
\titlespacing{\subsubsection}{0pt}{5pt}{3pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\ang}[1]{\left\langle {#1} \right\rangle}
\newcommand{\lc}{\left(}
\newcommand{\rc}{\right)}
\newcommand{\parentheses}[1]{\left({#1}\right)}
\newcommand{\pte}[1]{\left({#1}\right)}
\newcommand{\labs}{\left|}
\newcommand{\rabs}{\right|}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\op}{\operatorname}
\newcommand{\E}{\operatorname{E}}
\newcommand{\spt}{\operatorname{support}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}
\newcommand{\mC}{\mathcal{C}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mE}{\mathcal{E}}
\newcommand{\mJ}{\mathcal{J}}
\newcommand{\mK}{\mathcal{K}}
\newcommand{\mL}{\mathcal{L}}
\newcommand{\mM}{\mathcal{M}}
\newcommand{\mU}{\mathcal{U}}
\newcommand{\mV}{\mathcal{V}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\bZ}{\mathbb{Z}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bC}{\mathbb{C}}
\newcommand{\uge}{\succcurlyeq}
\newcommand{\Tr}{\op{Tr}}
\newcommand{\dd}{\mathrm{d}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%\begin{multicols}{3}
\section*{\textsc{Net Science}'s Sheet {\large by Feng Qiwei}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Biblographic Coupling}
	B.C. of $(i,j)$ is $\#$ of other nodes to which both $i,j$ point:
	$B=A^T A$.

\subsection{Degree}
	\[
		k_i=\# \textrm{ of edges connected to }i, \\
	\]
	\[
		\rho(G)=\frac{m}{\binom{n}{2}} = \frac{c}{n-1}\textrm{ where }c=\ang{k_i}.
	\]

\subsection{Transitivity}
	\[
	\textrm{clustering cofficient} =
		\frac{\#\textrm{ closed paths of len 2}} {\#\textrm{ paths of len 2}}, \\
	\]
	\[
	\textrm{local c.c.} =
		\frac{\#\textrm{ pairs of connected neighbors}} {\#\textrm{ pairs of neighbors}}.
	\]

\subsection{Centrality}
	\subsubsection{Eigenvector}
		Let $x(t)=A^t x(0)$ where $x(0)=\sum_i c_i v_i$,
		then $x(t)=\sum_i c_i \lambda_i^t v_i=\lambda_1^t \sum_i c_i (\lambda_i/\lambda_1)^tv_i$.
		For $t\to\infty$, know $(\lambda_i/\lambda_1)^t\to 0$ so $x(t)\to c_1\lambda_1^t v_1$, so
		\[
			\pte{Ax = \lambda_1 x} \Longrightarrow
			\pte{x_i=\lambda_1^{-1} \sum_j A_{ij} x_j}.
		\]
		\textbf{Prob.}
		Only vertices in out-component(s) of SCC of two or more vertices can have
			non-zero E.C..

	\subsubsection{Katz}
		\[
			\pte{x_i = \alpha\sum_j A_{ij} x_j + \beta}
			\Longleftrightarrow
			\pte{x=\alpha Ax+\beta 1}.
		\]
		Set $\beta=1$ (should have $\alpha<\lambda_1^{-1}$):
			$x=(I-\alpha A)^{-1} \cdot 1$.

	\subsubsection{Pagerank}
		\[
			\pte{x_i = \alpha \sum_j A_{ij} \frac{x_j}{k_j^{out}} + \beta}
			\Longleftrightarrow
			\pte{x=D(D-\alpha A)^{-1}\cdot \beta1}.
		\]

	\subsubsection{Hubs and Authorities}
		\[
			x=\alpha A y, y=\beta A^T x.
		\]

	\subsubsection{Closeness}
		\[
			d_{ij}=\textrm{ len of SP bet. $i$ and $j$},
			\textrm{~~~~}
			l_i=\frac{1}{n-1} \sum_{j\neq i} d_{ij},
			\textrm{~~~~}
			c_i=\frac{1}{l_i}.
		\]

	\subsubsection{Betweeness}
		\[
			n_{s,t}^i=\#\textrm{ of SP $s\to t$ through $i$},
			\textrm{~~~~}
			g_{s,t}=\#\textrm{ of SP $s\to t$},
		\] \[
			\textrm{B.C. of $i$}=x_i=\sum_{s,t} \frac{n_{s,t}^i}{g_{s,t}}.
		\]

	\subsubsection{Flow}
		\[
			x_i = \sum_{s,t} m_{s,t},
			\textrm{~~~~}
			m_{s,t}=\textrm{ flow through $i$ in a max $s$-$t$ flow}.
		\]

\subsection{Similarity}
	\textbf{Structral s.:} if share many of the same neighbors.
	\textbf{Regular s.:} if neighbors are similar.

	\subsubsection{Consine}
		\[
			\sigma_{ij} = \frac{\sum_k A_{ik} A_{kj}} {\sqrt{\sum_k A_{ik}^2}\sqrt{\sum_k A_{kj}^2}}
			=\textrm{(in unweight G)}=\frac{n_{ij}}{\sqrt{k_i k_j}}.
		\]
	\subsubsection{Pearson Coefficients}
		\[ \begin{split}
			\op{cov}(A_i,A_j)
			&= \#\textrm{common neighbors} - \#\textrm{exp. com. neighs} \\
			&= \sum_k A_{ik} A_{jk} - \frac{k_i k_j}{n} 
			= \sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}, \\
		\end{split} \]
		\[ \begin{split}
			r_{ij}
			&= \textrm{standard Pearson corellation coefficient} \\
			&= \frac{\sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}}
				{\sqrt{\pte{A_{ik}-\ang{A_i}}^2} \sqrt{\pte{A_{jk}-\ang{A_j}}^2}}. \\
		\end{split} \]

\subsection{Homiphily and Assortive Mixing}
	\subsubsection{A.M. by Enumerative Characteristics}
		\[ \begin{split}
			Q &= \textrm{modularity} \\
			&= \frac{1}{m} \pte{\#\textrm{same type edges} - \#\textrm{exp. same type edges}} \\
			&= \frac{1}{2m} \sum_{ij} \pte{A_{ij} - \frac{k_i k_j}{2m}} \delta(c_i,c_j)
			=\sum_r e_{rr} - a_r^2. \\
			e_{rs} &= \frac{1}{2m} \sum_{ij} A_{ij} \delta(c_i,r) \delta(c_j,s), \\
			a_r &= \frac{1}{2m} \sum_i k_i \delta(c_i,r). \\
		\end{split} \]

	\subsubsection{A.M. by Scalar Characteristics}
		\[ \begin{split}
			r &= \textrm{assortativity coefficient} \\
			&= \frac{\textrm{covariances over nodes}}{\textrm{cov. in perfectly mixed network}} \\
			&= \frac{\sum_{ij} \pte{A_{ij} - k_i k_j / 2m} x_i x_j}
				{\sum_{ij} \pte{k_i \delta_{ij} - k_i k_j /2m} x_i x_j}.
		\end{split} \]

\subsection{Power Law Distribution}
	\[
		p_k = C k^{-\alpha} \textrm{ where $\alpha$ in $[2,3]$ are typical}.
	\]
	\[
		P_k = \sum_{i=k}^\infty p_i
			\approx C \int_k^\infty x^{-\alpha} \dd x
			=\frac{C}{\alpha-1} k^{-(\alpha-1)}.
	\]
	\[ \begin{split}
		\alpha &= 1 + N\left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}, \\
		\sigma &= \sqrt{N} \left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}
			= \frac{\alpha-1}{\sqrt{N}}.
	\end{split} \]

\subsection{Graph Laplacian}
	Diffusion $\frac{\dd \psi_i}{\dd t}=c \sum_j A_{ij} (\psi_j-\psi_i)
		=c\sum_j(A_{ij}-\delta_{ij}k_i)\psi_j
		\Longrightarrow \frac{\dd \psi}{\dd t}=c(A-D)\psi$.
	Define $L=D-A$, then $\frac{\dd \psi}{\dd t}+cL\psi=0$.
	Need to solve $\psi(t)=\sum_i a_i(t) v_i$.
	Have $\sum_i (\frac{\dd a_i}{\dd t} + c\lambda_i a_i) v_i = 0$,
	then $\frac{\dd a_i}{\dd t} + c \lambda_i a_i=0$ since $v_i\perp v_j$.
	So $a_i(t)=a_i(0) e^{-c\lambda_i t}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Big Things}

\subsection{Random Graph}
	\subsubsection{Poisson Random Graph}
		Poisson r. g. $G(n,p)$:
		$n$ nodes where $\forall u,v$, $\Pr[\exists (u,v)\in G]=p$:
		\begin{itemize}
			\item mean $\#$ edges: $\binom{n}{2} p$;
			\item avg. deg.: $(n-1)p=c$;
			\item deg. distr.: $p_k=\binom{n-1}{k} p^k (1-p)^{n-1-k}$,
				and for large $n$: $p_k=e^{-c} \frac{c^k}{k!}$ (Poisson deg. distr.);
			\item cluster coefficient $= p = \frac{c}{n-1} \to 0$.
		\end{itemize}

	\subsubsection{Giant Component}
		$u$: fraction of vertices that do \textbf{NOT} belong to the giant $T$.
		If $i\notin T$, then $\forall j$, either
		\begin{itemize}
			\item $i$ is not connected to $j$: $1-p$;
			\item $i$ is connected to $j$ but $j\notin T$: $pu$.
		\end{itemize}
		Total: $1-p+pu$. Probability that $i\notin T$ is
		\[
			u=(1-p+pu)^{n-1}=\pte{1-\frac{c}{n-1}(1-u)}^{n-1},
		\]
		%= (n-1) \ln\pte{1-\frac{c}{n-1}(1-u)}
		\[
			\ln u 
			\approx -(n-1) \frac{c}{n-1} (1-u) = -c(1-u)
		\]
		\[
			\Longrightarrow u=e^{-c(1-u)}
			\Longrightarrow 1-u=S=1-e^{-cS}.
		\]
		Phase transition takes place when
		\[
			\left.\frac{\dd}{\dd S} \pte{1-e^{-cS}} = c e^{-cS} = 1 \right|_{S=0}
			\Longrightarrow c=1.
		\]
		Core $C(Q)$ and periphery $P(Q)$: $s=|C(Q)|+|P(Q)|$.
		A node in $P(Q)$ has $p(n-s)\approx c$ neighbors outside, so
		\[
			P(Q') \approx c P(Q), C(Q') = Q.
		\]
		If $c>1$, periphery grows; if $c<1$, it shrinks.

	\subsubsection{Small Components}
		$\pi_s$: prob that a randomly selected node belongs to a small component of size $s$.
		Fraction of nodes not in the giant: $\sum_{s=0}^\infty \pi_s = 1-S$.

		Observation: s.c. are trees.
		Consider tree of $s$ nodes.
		Remain place of edge: $\binom s 2 - (s-1) = \frac 1 2 (s-1)(s-2)$,
			so exp $\#$ non-tree edges: $\frac 1 2 (s-1)(s-2) p =
			\frac 1 2 (s-1)(s-2) c / (n-1) \to 0$,
			if $s$ increase slowly than $\sqrt n$.

		Consider $i$'s neighbors $n_1,...,n_k$ with component size $s_1,...,s_k$.
		$P(s|k)$: $i$ belongs to component of size $s$.
		\[
			P(s|k)=\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j).
		\]
		Know $\pi_s = \sum_{k=0}^\infty p_k P(s|k)$.
		(Generating function now!)
		Let $h(z)=\sum_{s=1}^\infty \pi_s z^s$,
			then $\pi_s=\left. \frac{1}{s!} \frac{\dd^s h}{\dd z^s} \right|_{z=0}$.
		Consider $h(z)$:
		\[ \begin{split}
			h(z) &= \sum_{s=1}^\infty z^s \sum_{k=0}^\infty p_k
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
			&= \sum_{s=1}^\infty z^s e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
			&= e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} z^{1+\sum_j s_j} \\
			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j} z^{s_j}} \\
			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\pte{\sum_{s=1}^\infty \pi_{s} z^{s}}^k 
			= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!} h^k(z) 
			= z e^{c(h(z)-1)}.
		\end{split} \]

		No closed-form solution for $h(z)$.
		$\ang{s}=\frac{\sum_s s\pi_s}{\sum_s \pi_s}=\frac{h'(1)}{1-S}$.
		Know
		\[
			h'(z)=e^{c(h(z)-1)} + czh'(z)e^{c(h(z)-1)} = \frac{h(z)}{z} + ch(z)h'(z)
		\]
		\[
			\Longrightarrow h'(z)=\frac{h(z)}{z(1-ch(z))}.
		\]
		$h(1)=\sum_s \pi_s=1-S \Longrightarrow \ang{s}=\frac{1}{1-c+cS}$.
		If $c<1$, no giant so $\ang{s}=\frac{1}{1-c}$.

		$n_s$: $\#$ components of size $s$. $\pi_s = s n_s/n$.
		Avg size of component: $$R=\frac{\sum_s s n_s}{\sum_s n_s}
			= \frac{n \sum_s \pi_s}{n \sum_s \pi_s / s}
			= \frac{1-S}{\sum_s \pi_s/s}.$$
		Noting that
		\[
			\int_0^1 \frac{h(z)}{z} \dd z = \sum_{s=1}^\infty \int_0^1 z^{s-1} \dd z
			= \sum_{s=1}^\infty \frac{\pi_s}{s}.
		\]
		Have $\frac{h(z)}{z} = (1-ch(z)) \frac{\dd h}{\dd z}$,
			so $$\sum_{s=1}^\infty \frac{\pi_s}{s}
			=\int_0^1 (1-ch(z)) \frac{\dd h}{\dd z} \dd z
			=\int_0^{1-S}(1-ch) \dd h = 1-S-\frac 1 2 c(1-S)^2.$$
		(Upper integration limit $ = h(1)= 1-S$.)
		Finally $R=\frac{2}{2-c+cS}$.
		(\textbf{NOTE:}
		$G(n,p)$ is connected if $p(n)=\frac{\log n}{n}$,
			then diameter $D=A+\frac{\ln n}{\ln c}$.)

	\subsubsection{Configuration Model}
		Specify degree distr $p$, randomly pick endpoints to form edges.

\subsection{Preferential Attachment}
	Each new paper cite $c$ old papers randomly:
	\[ \begin{split}
		p_q(n) &= \textrm{fraction of nodes with deg $q$}, \\
		q_i &= \textrm{in-degree of node $i$}, \\
	\end{split} \]
	\[
		\Pr[i\textrm{ get citation}] = \frac{q_i+a}{\sum_j (q_j+a)} = \frac{q_i+a}{n(c+a)}. \\
	\]
	\[
		\E[\textrm{new cites deg $q$ nodes}]
			=n p_q(n) c \frac{q+a}{n(c+a)} = \frac{c(q+a)}{c+a} p_q(n).
	\]
	\subsubsection{Master Equation}
		\[ \begin{split}
			(n+1)p_q(n+1)&=np_q(n)
				+\frac{c(q-1+a)}{c+a}p_{q-1}(n)- \frac{c(q+a)}{c+a}p_q(n) \\
			(n+1)p_0(n+1)&=np_0(n)+1-\frac{ca}{c+a}p_0(n).
		\end{split} \]
		\[
			n\to\infty\Longrightarrow
			p_0=\frac{1+\frac{a}{c}}{a+1+\frac{a}{c}},
			p_q=\frac{q+a-1}{q+a+1+\frac{a}{c}}p_{q-1},
		\]
		\[
			\Longrightarrow
			p_q=\frac{(q+a-1)(q+a-2)\cdots a}{(a+a+1+\frac{a}{c})\cdots(a+1+\frac{a}{c})}.
		\]
		% TODO: Gamma Beta
		For large $q$,
			$p_q\sim (q+a)^{-\alpha}$ or simply $p_q\sim q^{-\alpha}$,
			where $\alpha=2+\frac{a}{c}$.

	\subsubsection{Mean-Field Approximation}
		One link with $p$ choose uniform, $q=1-p$ choose by P.A..
		\[ \begin{split}
			x_i(t) &= \textrm{in-degree of $i$ at time $t$ with $x_i(i)=0$}, \\
			\Delta_t &= \E[x_i(t+1)-x_i(t)]  = \frac{p}{t} + \frac{(1-p)x_i(t)}{t}.
		\end{split} \]
		Consider a deterministic process in which a nodes degree increased by exact $\Delta_t$.
		Find distribution of expected degrees.
		\[
			d_i(i) = 0, \frac{\partial d_i(t)}{\partial t} = \frac{p}{t} + \frac{(1-p)d_i(t)}{t}.
		\]
		\[
			\Longrightarrow \int \frac{1}{p+q d_i} \frac{\partial d_i}{\partial t} \dd t = \int \frac{1}{t} \dd t \\
		\] \[
			\Longrightarrow \ln(p+q d_i) = q \ln t + c \\
		\] \[
			\Longrightarrow p+q d_i = A t^q, \\
		\] \[
			\textrm{set $d_i(i)=0$,}\Longrightarrow d_i(t) = \frac{p}{q}\pte{\pte{\frac{t}{i}}^q-1}.
		\]
		$i_t(k)$: node with expected degree exactly $k$ at time $t$:
		\[
			d_{i_t(k)}(t) = k = \frac{p}{q}\pte{\pte{\frac{t}{i_t(k)}}^q-1}
			\Longrightarrow
			i_t(k)=t\pte{\frac{p}{q}k+1}^{-\frac{1}{q}}.
		\]
		Fraction of nodes with degree $>k$:
			$F_k(t) = \pte{\frac{q}{p}k+1} ^ {-\frac{1}{q}}$,
		\[
			\Longrightarrow
			p_k=-\frac{\partial F_k}{\partial k}
			=\frac{1}{p}\pte{\frac{q}{p}k+1}^{-1-\frac{1}{q}}
			\sim k^{-\pte{1+\frac{1}{q}}}.
		\]

\subsection{Small World}
	Each node is connected with all neighbors of distance $\le c/2$.
	For $nc/2$ times pick random pair and add shortcut w.p. $p$.

	\subsubsection{Degree Distribution}
		\[
			k_i = c + s_i = c + (\#\textrm{shortcuts attacked to $v_i$}).
		\]
		There are $ncp$ endpoints of shortcuts. $s_i$ is Poisson distributed
			with mean $cp$:
		\[
			p_s = e^{-cp}\frac{(cp)^s}{s!} \Longrightarrow
			p_k = e^{-cp}\frac{(cp)^{k - c}}{(k - c)!}, \textrm{ for }k \ge c.
		\]

	\subsubsection{Clustering Coefficient}
		$C=(\#\textrm{triangles}\times 3)/(\#\textrm{connected tripes})$.
		\begin{enumerate}
			\item $\#$ triangles
			\begin{enumerate}
				\item in ring: $n\binom{c/2}{2}=\frac{1}{4}nc(\frac{c}{2} - 1)$.
				\item due to shortcuts:
					prob $u,v$ connected by shortcut$=\frac{ncp/2}{n(n-1)/2}\approx \frac{cp}{n}$.
					A shortcut complete a triangle for $u,v$ with dist $\frac{c}{2}\sim c$,
						$\#$ of such $u,v$ is proportional to $n$.
					$\Longrightarrow \sim n\cdot \frac{cp}{n} = cp =$
					const $\to$ ignore.

			\end{enumerate}
			\item $\#$ connected tripes
			\begin{enumerate}
				\item in ring: $n\binom{c}{2}=\frac{1}{2}nc(c - 1)$.
				\item through shortcuts: $(ncp/2)\times 2\times c$.
				\item through pairs of shortcuts: for node with $m$ shortcuts,
					has $\binom{m}{2}$ triples.
					Let $m=cp$ (mean of Poisson distr) then total triples
					$=(nc^2p^2)/2$.
			\end{enumerate}
		\end{enumerate}
		\[
			C=\frac{3(c-2)}{4(c-1)+8cp+4cp^2}.
		\]

	\subsubsection{Path length}
		No exact expr for mean distance in WS model.
		Consider $c=2$. Let $l=$ average len of SP.
		$s=\#$ shortcuts.

		Avg dist between shortcuts on ring $\tau=\frac{n}{2s}$
			$\Longrightarrow$ $n,\tau$ completely specify the model.

		Consider dimensionless $\frac{l}{n}$.
		$\frac{l}{n}=F(\frac{n}{\tau})=F(2s)$
		($F$: universal).
		If density of shortcuts is low then for general $c$:
		$l=\frac{2n}{c} F(2s) = \frac{n}{c} f(ncp)$.
		Simulate $f$:
		\[
			f(x) = \frac{2}{\sqrt{x^2+4x}}\op{tanh}^{-1}\sqrt{\frac{x}{x+4}}
		\]
		\[
			\Rightarrow x\to\infty
			\Rightarrow f(x) = \frac{\ln x}{x}
			\Rightarrow l = \frac{\ln(ncp)}{c^2p}.
		\]

	\subsubsection{Milgram}
		Short paths exists and can be found efficiently in decentralized way.
		WS model: $c=2$; $K=$ nodes with dist $\le\sqrt{n}$ of $t$.
		$\Pr[\textrm{a shortcut points into $K$}]=2/\sqrt{n}$
			$\to$ need at least $\sqrt{n}/2$ steps into $K$.
		Crossing $K$ step-by-step at least $\sqrt{n}/2$ steps.
		Thus need $\Omega(\sqrt n)$ steps.

	\subsubsection{Kleinberg}
		Choose shortcuts s.t.
			$\Pr[\textrm{shortcut between $u,v$ at dist $r$}]=\kappa r^{-\alpha}$.
		Choose shortcut len from distribution.
		Place edge randomly in network.
		Total prob that shortcut between two nodes is $p\kappa r^{-\alpha}$.
		Normalization const $\kappa$:
		\[
			\kappa\sum_{r = 1}^{\frac{1}{2}(n - 1)}r^{-\alpha} = 1.
		\]
		We can approximate the sum:
		\[
			\sum\limits_{r= 1}^{\frac{1}{2}(n - 1)} r^{-\alpha}
			\approx\int_{1}^{\frac{1}{2}(n - 1)} r^{-\alpha}\dd r
			+\frac{1}{2}+\frac{1}{2}\pte{\frac{1}{2}(n - 1)}^{-\alpha},
		\]
		where $\int_{1}^{(n - 1)/2} r^{-\alpha}\dd r=((n-1)/2)^{1-\alpha}/(1-\alpha)$.
		For $n\to\infty$:
		\[
			\kappa\approx\left\{\begin{array}{ll}
				(1-\alpha)(\frac{1}{2}n)^{\alpha - 1} &\alpha<1\\
				\ln^{-1}(\frac{1}{2}n) &\alpha = 1\\
				\frac{2(\alpha-1)}{\alpha+1} &\alpha>1
			\end{array}\right..
		\]
		Divide nodes into classes that $C_k$ consists of $v_i$ with
			$2^{k-1}\le d(v_i,t)<2^k$.
		Nodes in $C_0,...,C_{k-1}$:
			$\sum_{m=0}^{k-1}n_m = \sum_{m=0}^{k-1}2^m = 2^k-1 > 2^{k-1}$.
		All these are at most a dist $3 * 2^k < 2^{k+2}$ from $v_{\mathrm{cur}}$ in $C_k$.
		Prob of having a shortcut to one of the nodes:
		\[
			p\kappa 2^{-(k+2)\alpha}*2^{k-1}=p\kappa 2^{k-1-(k+2)\alpha}.
		\]
		If $v_{\mathrm{cur}}$ has no shortcut, pass msg to neighbor.
		Exp $\#$ moves until find a shortcut to $C_0,...,C_{k-1}$ is 
		\[
			\frac{1}{p\kappa} 2^{2\alpha+1} 2^{(\alpha-1)k}.
		\]
		In wrost case msg goes through all classes:
		\[
			l \le \frac{1}{p\kappa}*2^{2\alpha+1}*
				\sum_{k=0}^{\log(m+1)}2^{(\alpha-1)k}
			= \frac{1}{p\kappa}*2^{2\alpha+1}
				\frac{(2(n+1))^{\alpha-1}-1}{2^{\alpha-1}-1}.
		\]
		Plugging the value of $\kappa$ for $n\to\infty$:
		\[
			l=\left\{\begin{array}{ll}
				A n^{1-\alpha} &\alpha<1\\
				B \log^2 n &\alpha = 1\\
				C n^{\alpha-1} &\alpha>1
			\end{array}\right..
		\]

\subsection{Stable Outcome}
	\subsubsection{Nash Bargain Solution}
		$A$ and $B$ with outside option $x$ and $y$.
		If $x+y>1$ then no agreement possible.
		If $x+y\le 1$ then has surplus $s=1-x-y$.

		NBS: devide surplus evenly.

	\subsubsection{Stable Outcome}
		$G=(V,E)$, edge weight $w:E\to R^+$. Each $v\in V$ is a player.

		\textbf{Outcome}: matching $M$ among players and vector $x$
			describing each players payoff.
			$\forall(u,v)\in M$, $x_u+x_v=w_{u,v}$; $\forall u\notin M$, $x_u=0$.

		\textbf{Stable outcome}: outcome with no unstable edge.

		\textbf{Balanced outcome} (generalization of NBS):
			$\forall (u,v)\in M$, split of money represents the NBS
				for $u,v$ given the best outside option for $u,v$
				provided by values in the rest of the network.

>>>>

\documentclass[12pt,abstract=true]{scrartcl}

%<<< Preamble
\usepackage{tikz}
\usepackage{array}
\usepackage{pifont}
\usepackage{engord}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[plain]{fancyref}
\usepackage[unicode]{hyperref}
\usepackage{graphicx,tabularx}
\usepackage[shortlabels]{enumitem}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
\usepackage{mathtools}
\usepackage{exscale}
\usepackage{relsize}
\usepackage{mathrsfs}

\usepackage{setspace}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}

\usepackage{lmodern}
\usepackage{mathpazo}

\pgfplotsset{compat=1.6}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usepackage{tikz-3dplot}

\tikzset{ alert/.style={ very thick, draw=red!80, fill=red!20 } }
\tikzset{ fancy/.style={ very thick, draw=blue!80, fill=blue!20 } }
\tikzset{
  dot/.style={
    very thick,circle,draw=black,fill=black,inner sep=0,minimum size=5pt
  }
}
\tikzset { every state/.style={fancy} }
\tikzset {
  general/.style = {
    shorten >=2pt, node distance=2.5cm, on grid, thick,>=stealth', auto
  }
}
\newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
\newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}

\newcommand\Mark[1]{\textsuperscript#1}
\numberwithin{equation}{section}
\mathtoolsset{centercolon}
\bibliographystyle{plain}

% Theorem environment <<<
\theoremstyle{definition}   \newtheorem{definition}{Definition}[section]
\theoremstyle{plain}        \newtheorem{theorem}{Theorem}[section]
\theoremstyle{plain}        \newtheorem{observation}{Observation}[section]
\theoremstyle{plain}        \newtheorem{fact}{Fact}[section]
\theoremstyle{plain}        \newtheorem{claim}{Claim}[section]
\theoremstyle{plain}        \newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{plain}        \newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{remark}       \newtheorem{example}{Example}[section]
\theoremstyle{remark}       \newtheorem{remark}{Remark}[section]
\newcommand*{\fancyrefdeflabelprefix}{def}
\newcommand*{\fancyrefthmlabelprefix}{thm}
\newcommand*{\fancyreflemlabelprefix}{lem}
\newcommand*{\fancyrefcorlabelprefix}{cor}
\newcommand*{\fancyrefalglabelprefix}{alg}
\newcommand*{\fancyreflnlabelprefix}{ln}
\frefformat{plain}{\fancyreflnlabelprefix}{line #1}
\Frefformat{plain}{\fancyreflnlabelprefix}{Line #1}
\frefformat{plain}{\fancyrefalglabelprefix}{algorithm (#1)}
\Frefformat{plain}{\fancyrefalglabelprefix}{Algorithm (#1)}
\frefformat{plain}{\fancyrefdeflabelprefix}{definition (#1)}
\Frefformat{plain}{\fancyrefdeflabelprefix}{Definition (#1)}
\frefformat{plain}{\fancyrefthmlabelprefix}{theorem (#1)}
\Frefformat{plain}{\fancyrefthmlabelprefix}{Theorem (#1)}
\frefformat{plain}{\fancyreflemlabelprefix}{lemma (#1)}
\Frefformat{plain}{\fancyreflemlabelprefix}{Lemma (#1)}
\frefformat{plain}{\fancyrefcorlabelprefix}{corollary (#1)}
\Frefformat{plain}{\fancyrefcorlabelprefix}{Corollary (#1)}
%>>>
% Alter some LaTeX Float for better treatment of figures: <<<
% See p.105 of "TeX Unbound" for suggested values.
% See pp. 199-200 of Lamport's "LaTeX" book for details.
%   General parameters, for ALL pages:
\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

\allowdisplaybreaks[4]

%>>>
%>>>

\begin{document}

\begin{center} %<<< Title
	\Large \textbf{\textsf{
		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
	\small
		Pufan He\Mark{1}, Yichao Zhou\Mark{2}, Qiwei Feng\Mark{3},
		Yu Yan\Mark{4}, Qingyang Li\Mark{5} and Xin Xing\Mark{6}\\[1em]
	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
		\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
		\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
		\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline

		\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
		\href{mailto:591527324@qq.com}{591527324@qq.com} &
		\href{mailto:823291634@qq.com}{823291634@qq.com}
	\end{tabular} \\[1em]

	\normalsize IIIS, Tsinghua University \\[1em]
\end{center} \par %>>>

\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered as vertex while relation is considered as edge. We suppose the
evolution of a social network overtime only includes bidirectional new
connections between existing or newly created nodes, and we assume the graph
will evolve as a typical social network. We study the centrality and activity
metrics for nodes in such graphs by regulate a series of reasonable properties
the metrics should satisfy. We then formally define our metrics and give their
mathematical analysis. We have developed a practical based framework to
maintain the evolving network and the algorithm to compute our metrics with
preferable time and space consumption, including historical queries. Finally,
we put the result of experiment with a couple of authentic data.

\smallskip
\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
activity, algorithm.
\end{abstract}

\section{Introduction}
social network 
\section{}
\section{}
\section{Conclusion}
\nocite{*}
\bibliography{paper.bib}
\end{document}

% vim: set ts=8 sw=8 noet sts=8 tw=79 indentexpr= fdm=marker foldmarker=<<<,>>>:
